---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dramatis.personae

<!-- badges: start -->
<!-- badges: end -->

This package generates a YAML file for gathering authors and their affiliations then uses that file to generate a list of authors and their affiliations for manuscripts.

## Installation

You can install the development version of dramatis.personae from [GitHub](https://github.com/) with:

```r
devtools::install_github("raykrajci/dramatis.personae")
```

## Example

Generating the list of authors and their affiliations is a two step process:

```{r}
# Generate the YAML file.
# Defaults to "dramatis.personae.yaml" in the working directory.

dramatis.personae::initialize()

# Generate the list of authors and affiliations from the YAML file.

result <- dramatis.personae::generate()

result$authors

result$affiliations

```
